---
title: "p8105_hw1_jz3571"
author: "Junyan Zhu"
date: "2022-09-21"
output: github_document
---

# Problem 1 

## download and load library dataset

```{r}
library(tidyverse)
library(ggplot2)
library(palmerpenguins)
data("penguins", package = "palmerpenguins")
```

## Look at the data

### Important variables
```{r}
summary(penguins)
names(penguins)
```

There are seven variables in total in the dataset of penguins. There are three species of penguins living in three islands. The bill length, bill depth, flipper length, body mass, sex and year are recorded.

### Size of dataset
```{r}
nrow(penguins)
ncol(penguins)
```

There are 344 rows and 8 columes in the dataset

### Mean of flipper length

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The mean of flppper length in mm is about 200.9.

## Scatterplot of flipper length and bill length

### Make the scatterplot

```{r}
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggp = ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

### Save the scatterplot


```{r}
ggsave(filename = "scatterplot_of_penguins.pdf", plot = ggp)
```

# Problem 2

## Creat a data frame

```{r}
samp_df = tibble (
  var_num = rnorm(10, mean = 0, sd = 1),
  var_logic = var_num > 0,
  var_vector = c("a","b","c",'d','e','f','g','h','i','j'),
  var_factor = factor(c("1", "2", "3",'1','2','3','1','2','3','1'))
)
```

