---
title: "p8105_hw1_jz3571"
author: "Junyan Zhu"
date: "2022-09-21"
output: github_document
---

# Problem 1 

## download and load library dataset

```{r, message = FALSE}
library(tidyverse)
library(ggplot2)
library(palmerpenguins)
data("penguins", package = "palmerpenguins")
```

## Look at the data

### Important variables
```{r}
summary(penguins)
names(penguins)
```

There are 8 variables in total in the dataset of penguins describing species, islands, bill length in mm, bill depth in mm, flipper length in mm, body mass in g, sex and year.

### Size of dataset
```{r}
nrow(penguins)
ncol(penguins)
```

There are 344 rows and 8 columes in the dataset

### Mean of flipper length

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

After dropping the two missing data, the mean of flppper length in mm is about 200.9.

## Scatterplot of flipper length and bill length

### Make the scatterplot

```{r}
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggp = ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

### Save the scatterplot


```{r}
ggsave(filename = "scatterplot_of_penguins.pdf", plot = ggp)
```

# Problem 2

## Creat a data frame

```{r}
samp_df = tibble (
  var_num = rnorm(10, mean = 0, sd = 1),
  var_logic = var_num > 0,
  var_vector = c("a","b","c",'d','e','f','g','h','i','j'),
  var_factor = factor(c("1", "2", "3",'1','2','3','1','2','3','1'))
)
```

## Mean of each variable

```{r}
#mean of numeric variable
mean(samp_df$var_num)
#mean of logical variable
mean(samp_df$var_logic)
#mean of character variable
mean(samp_df$var_vector)
#mean of factor variable
mean(samp_df$var_factor)
```

We can get a mean from numerical and logcial variable respectively, but we cannot take means form character and factor variable

## Apply `as.numeric

`
```{r, results = "hide"}
#mean of logical variable
mean(as.numeric(samp_df$var_logic))
#mean of character variable
mean(as.numeric(samp_df$var_vector))
#mean of factor variable
mean(as.numeric(samp_df$var_factor))
```

Now we can get a mean from logical and factor variable, but still cannot from the character variable. This is because we can only get a mean from numerical values. In this case, the factor variable is converted to numerical variable based on its level, while for character variable such convertion is unable to made.
